Empirical normative theories

### 2020-07-21 simple.tex
Some heuristic note about bootstrap (zar); and cosmetic changes

Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeats \ar_0$ iff $\exists \hist \in \allhist \suchthat \ar_1 \in (\gbeatsinv(\ar_0) \cap \hist) \land \ar_0 \in \histend \land \hist \nileadsto \phi \land (\gbeatsinv(\ar_0) \cap \hist) \setminus \set{\ar_1} \sinef \ar_0$.

@@

	Given any $\ar_0 \in \allargs$, define $\args^{\hist} = \gbeatsinv(\ar_0) \cap \hist$ and $\allhistsznp = \set{\hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi}$. Given $\hist \in \allhistsznp$, say that $\hist$ is \emph{reducible} iff $\hist \in \allhistred$, defined as $\allhistred = \set{\hist \in \allhistsznp \suchthat \forall \ar_1 \in \args^{\hist}: \args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0}$; define accordingly $\allhistnonred = \allhistsznp \setminus \allhistred = \set{\hist \in \allhistsznp \suchthat \exists \ar_1 \in \args^{\hist} \suchthat \args^{\hist} \setminus \set{\ar_1} \sinef \ar_0}$.

	Lemma: given any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$, if $\allhistsznp ≠ \emptyset$, $\hist \in \allhistred ⇒ \exists \histp \in \allhistsznp \suchthat \emptyset ≠ \args^{\histp} \subset \args^{\hist}$. To see this, pick as $\histp$ any sequence consisting of the arguments contained in $\args^{\hist} \setminus \set{\ar_1}$, followed by $\ar_0$. 
	First, $\histp \in \allhistsznp$, because as $\hist \in \allhistred$, $\args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0$, thus, $\histp \nileadstost \phi$. 
	Second, $\args^{\histp} = \args^{\hist} \setminus \set{\ar_1}$, because $\args^{\hist} \setminus \set{\ar_1} \subseteq \args^{\histp} = \left(\gbeatsinv(\ar_0) \cap \histp\right) \subseteq \args^{\hist} \setminus \set{\ar_1}$.
	Finally, $\args^{\histp} ≠ \emptyset$ follows from two facts: that $\args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0$ (see “First” here above) and that $\emptyset \sinef \ar_0$, which is implied by $\ar_0$ $i$-defends $\phi$.

@@

Consider $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto \phi$. Test whether $(\ar_0) \ileadstost \phi$. If not, $(i, \phi, (\ar_0))$ is a falsification instance of $\gamma$. If $(\ar_0) \ileadsto \phi$, check whether some $\ar_1 \dbeats' \ar_0$. If not, $\delta$ is falsified? ($\ar_0$ attacks $\delta$ but $\delta$ is not able to defend.)…

>>>>

Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeats \ar_0$ iff $\exists \hist \in \allhist \suchthat 
	\ar_1 \in (\gbeatsinv(\ar_0) \cap \hist) \land 
	(\gbeatsinv(\ar_0) \cap \hist) \setminus \set{\ar_1} \sinef \ar_0 \land 
	\ar_0 \in \histend \land 
	\hist \nileadsto \phi$.

@@

	Given any $\ar_0 \in \allargs$, define $\args^{\hist} = \gbeatsinv(\ar_0) \cap \hist$ and $\allhistsznp = \set{\hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi}$. Given $\hist \in \allhistsznp$, say that $\hist$ is \emph{reducible} iff $\hist \in \allhistred = \set{\hist \in \allhistsznp \suchthat \forall \ar_1 \in \args^{\hist}: \args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0}$; define accordingly $\allhistnonred = \allhistsznp \setminus \allhistred = \set{\hist \in \allhistsznp \suchthat \exists \ar_1 \in \args^{\hist} \suchthat \args^{\hist} \setminus \set{\ar_1} \sinef \ar_0}$.

	Lemma: given any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$, if $\allhistsznp ≠ \emptyset$, then $\hist \in \allhistred ⇒ \exists \histp \in \allhistsznp \suchthat \emptyset ≠ \args^{\histp} \subset \args^{\hist}$. To see this, pick as $\histp$ any sequence consisting of the arguments contained in $\args^{\hist} \setminus \set{\ar_1}$, followed by $\ar_0$. 
	First, $\histp \in \allhistsznp$, because as $\hist \in \allhistred$, $\args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0$, thus, $\histp \nileadstost \phi$. 
	Second, $\args^{\histp} = \args^{\hist} \setminus \set{\ar_1}$, because $\args^{\hist} \setminus \set{\ar_1} \subseteq \args^{\histp} = \left(\gbeatsinv(\ar_0) \cap \histp\right) \subseteq \args^{\hist} \setminus \set{\ar_1}$.
	Finally, $\args^{\histp} ≠ \emptyset$ follows from two facts: that $\args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0$ (see “First” here above) and that $\emptyset \sinef \ar_0$, which is implied by $\ar_0$ $i$-defends $\phi$.

@@

\begin{remark}
	$\allargs \setminus \gleadstoinv(\phi)$ are the non-initial arguments. An empirical theory must satisfy: $\dbeats$ covers all attackers and $\allargs \setminus \gleadstoinv(\phi)$. Note that $\ar'_0 \gbeats \ar_0$ seems possible (thus, an attacker not in $\allargs \setminus \gleadstoinv(\phi)$), and $\zar$ not attacking anything but in $\allargs \setminus \gleadstoinv(\phi)$ is possible, where $\zar$ designates an argument that says nothing.

	If $\hist$ does not include any initial argument, and includes $\ar_1$, and leads to $¬\phi$, then proceed as if $\ar_1$ attacks $\emptyset$, thus, include the defensor against $\ar_1$. This defensor must be in $\allargs \cap \alldargs$. (It’s probably better to remove the $\alldargs$ concept.)
\end{remark}

Consider $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto \phi$. Test whether $(\ar_0) \ileadstost \phi$. If not, $(i, \phi, (\ar_0))$ is a falsification instance of $\gamma$. If $(\ar_0) \ileadstost \phi$, check whether some $\ar_1 \dbeats' \ar_0$. If not, $\delta$ is falsified? ($\ar_0$ attacks $\delta$ but $\delta$ is not able to defend.)…
